### 2025-10-06 conteudo/results/eval.tex
fix typo

>>>>

\subsection{Performance Evaluation of the Tool}

Our performance evaluation on a Ryzen 5700X machine with 32GB of RAM shows the tool's efficiency. 
During testing, the offline Preprocessor's longest run was 8 minutes and 56 seconds for the AMD Display driver 
and 9 minutes and 41 seconds for the IIO subsystem. By contrast, the online Query Responder handled all user
requests in less than 2 seconds. This result confirms the value of separating the time-consuming analysis 
from the real-time query phase.
